Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-10-15 src/tex/appendicies.tex
add ppc plot and some tables to try and make results presentation cleaner and more complete

\begin{table*}[hb!]
    \centering
    \begin{tabular}{|l|l|l|l|}
    \hline
    \textbf{Model} & \textbf{Parameter} & \textbf{Description} & \textbf{Prior} \\ \hline \hline
    \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,100) \\ \cline{2-4}
     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 64 \\ \cline{2-4} 
    \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4}  
    \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
    \textsc{PowerLaw+B-Spline} & $\lambda$ & slope of redshift evolution power law $(1+z)^\lambda$ &  $\sim \mathcal{N}(0,3)$ \\ \cline{2-4}
    & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
    \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
    \textsc{B-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
    & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4} 
    \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
    & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
    \end{tabular}
    \caption{All hyperparameter prior choices for each of the newly introduced basis spline models from this manuscript. See appendix 
    \ref{sec:basis_splines} and \ref{sec:psplines} for more detailed description of basis spline or smoothing prior parameters.}
    \label{tab:model_priors}
\end{table*}

>>>>

\begin{table*}[hb!]
    \centering
    \begin{tabular}{|l|l|l|l|}
    \hline
    \textbf{Model} & \textbf{Parameter} & \textbf{Description} & \textbf{Prior} \\ \hline \hline
    \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
    \textsc{B-Spline Primary} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,100) \\ \cline{2-4}
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 6 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 64 \\ \hline \hline 
    \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
    \textsc{B-Spline Ratio} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 3 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 18 \\ \hline \hline
    \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
    \textsc{PowerLaw+B-Spline} & $\lambda$ & slope of redshift evolution power law $(1+z)^\lambda$ &  $\sim \mathcal{N}(0,3)$ \\ \cline{2-4}
    & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 16 \\ \hline \hline 
    \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
    \textsc{B-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$  \\ \cline{2-4} 
    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
    & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
    & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
    & $n$ & number of knots in the basis spline & 18 \\ \hline \hline 
    \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$  \\ \cline{2-4} 
    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
    & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
    & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
    & $n$ & number of knots in the basis spline & 16 \\ \hline \hline
    \end{tabular}
    \caption{All hyperparameter prior choices for each of the newly introduced basis spline models from this manuscript. See appendix 
    \ref{sec:basis_splines} and \ref{sec:psplines} for more detailed description of basis spline or smoothing prior parameters.}
    \label{tab:model_priors}
\end{table*}

### 2022-10-15 src/tex/results.tex
changes to conclusions
fix few redshift sentences
add ppc plot script
add ppc plot and some tables to try and make results presentation cleaner and more complete

\begin{figure}
    \begin{centering}    
        \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
        \caption{The spin magnitude distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from 0 to 1, assuming the components are IID. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:iid_spinmag_dist}
    \end{centering}
    \script{plot_iid_spinmag.py}
\end{figure}

@@

\begin{figure} 
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spinmag_dist}
    \end{centering}
    \script{plot_ind_spinmag.py}
\end{figure}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spintilt_dist}
    \end{centering}
    \script{plot_ind_spintilt.py}
\end{figure}

@@

@@

>>>>

\begin{figure}
    \begin{centering}    
        \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
        \caption{The spin magnitude distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from 0 to 1, assuming the components are IID. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:iid_spinmag_dist}
    \end{centering}
    \script{plot_iid_spinmag.py}
\end{figure}

@@

\begin{figure} 
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spinmag_dist}
    \end{centering}
    \script{plot_ind_spinmag.py}
\end{figure}

\begin{table*}[ht!]
    \centering
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        Model & $a_\mathrm{peak}$ & $a_\mathrm{90\%}$ & $\cos{\theta_\mathrm{peak}}$ & $f_{\cos{\theta}<0}$ & $\log_{10}Y$ \\ \hline \hline
        B-Spline IID & $\CIPlusMinus{\macros[BSplineIIDCompSpins][peak_a]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][peakCosTilt]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][negFrac]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][log10gammaFrac]}$ \\ \hline
        B-Spline Ind(primary) & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peak_a1]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][a1_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt1]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac1]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac1]}$ \\ \hline
        B-Spline Ind(secondary) & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peak_a2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][a2_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac2]}$  \\ \hline
        \textsc{Default} & $\CIPlusMinus{\macros[Default][peak_a]}$ & $\CIPlusMinus{\macros[Default][a_90percentile]}$ & $\CIPlusMinus{\macros[Default][peakCosTilt]}$ & $\CIPlusMinus{\macros[Default][negFrac]}$ & $\CIPlusMinus{\macros[Default][log10gammaFrac]}$ \\ \hline
    \end{tabular}
    \caption{Summary of Component Spin distributions inferred both the independent and IID component spin B-Spline models and the \textsc{Default} spin model from \citet{o3b_astro_dist}.}
    \label{tab:compspins}
\end{table*}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spintilt_dist}
    \end{centering}
    \script{plot_ind_spintilt.py}
\end{figure}

@@

\begin{table*}[ht!]
    \centering
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        Model & $\chi_\mathrm{eff,peak}$ & $f_{\chi_\mathrm{eff}<0}$ & $f_{\chi_\mathrm{eff}<-0.3}$ & $f_\mathrm{dyn}$ & $f_\mathrm{HM}$ \\ \hline \hline
        B-Spline IID & $\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][frac_hm]}$ \\ \hline
        B-Spline Ind & $\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][frac_hm]}$ \\ \hline
        \textsc{Default} & $\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_hm]}$ \\ \hline
        \textsc{Gaussian} & $\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_hm]}$ \\ \hline
    \end{tabular}
    \caption{Summary of the effective spin distributions inferred with the B-Spline model variations, along with the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}.}
    \label{tab:chieff}
\end{table*}

@@

\subsection{Posterior Predictive Checks} \label{sec:ppcs}

\begin{figure*}[ht!]
    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
    \caption{Posterior Predictive Check}
    \label{fig:ppc}
    \script{plot_ppcs.py}
\end{figure*}

Here we describe our posterior predictive checking procedure and results shown in figure \ref{fig:ppc}.
